---
title: "mpbPine"
author:
  - "Alex M. Chubaty"
  - "Barry J. Cooke"
  - "Eliot J. B. McIntire"
date: "May 25, 2021"
output:
  html_document:
    keep_md: yes
    toc: true
    toc_depth: 3
    toc_float: true
bibliography:
  - bibliography.bib
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE, results = "hold")
```

# Overview

Download and use proportion pine data, based on provincial forest inventory data and prepared for the updated MPB Risk Assessment [@Bleiker:2019].
These data cover most of the managed boreal forests in Alberta and Saskatchewan.

In the current model, we calculate the number of available jack pine and lodgepole pine trees from the proportion pine for each species, by multiplying by the average stem density of 1125 mature stems per hectare, which is typical for beetle-prone lodgepole pine stands [@Whitehead:2004rz; @Cooke:2017fem].

A more sophisticated estimate of pine stem density for each species is currently under development for future versions of this module.

# Usage

```{r module_usage}
library(SpaDES.core)

setPaths(modulePath = file.path(".."))
getPaths() # shows where the 4 relevant paths are

times <- list(start = 0, end = 10)

parameters <- list(
  #.progress = list(type = "text", interval = 1), # for a progress bar
  ## If there are further modules, each can have its own set of parameters:
  #module1 = list(param1 = value1, param2 = value2),
  #module2 = list(param1 = value1, param2 = value2)
)
modules <- list("mpbPine")
objects <- list()
inputs <- list()
outputs <- list()

mySim <- simInit(times = times, params = parameters, modules = modules,
                 objects = objects)

mySimOut <- spades(mySim)
```

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams, echo = FALSE, eval = TRUE}
df_params <- SpaDES.core::moduleParams("mpbPine", "..")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("mpbPine", "..")` may be sufficient.

```{r moduleInputs, echo = FALSE, eval = TRUE}
df_inputs <- SpaDES.core::moduleInputs("mpbPine", "..")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs, echo = FALSE, eval = TRUE}
df_outputs <- SpaDES.core::moduleOutputs("mpbPine", "..")
knitr::kable(df_outputs)
```

# Links to other modules

Part of the `LandR_MPB` Mountain Pine Beetle Red Top Model, which evaluates short-run potential for MPB establishment, eruption, and spread.

- `mpbClimateData`
- `mpbMassAttacksData`
- `mpbPine`
- `mpbRedTopSpread`

Future linkages include the `LandR` Biomass suite of modules to simulate/forecast forest vegetation dynamics, and the `fireSense` wildfire simulation model.

# References
